Approximation as Differentiation: Notes

### 2025-07-04 notes/predicate-system.tex
Ok, natural isomorphism between C \comp -[f] and -[f] \comp C is just the statement that C is a fibred functor.
Assuming closure operator over a predicate system is a monad (but we don't have that data in the Agda).

>>>>

\subsubsection{Closure operator over a predicate system}

A \emph{closure operator} $C$ over a poset $(X, \sqleq)$ is a lax idempotent monad on $X$, with functoriality,
unit and multiplication given by monotonicity, extensivity ($x \sqleq C(x)$) and idempotence ($C(C(x)) \sqleq
C(x)$).

Suppose $\mathcal{S} = (\Pred, \top, \meet, \join, \residual, \forall)$ a predicate system over a category
$\cat{C}$. A closure operator $C$ over $\mathcal{S}$ is a fibred lax idempotent monad $C$ on the fibration
$\Pred: \cat{C}^\op \to \Poset$ where for every object $X$ the fibre map $C_X: \Pred(X) \to \Pred(X)$ is a
closure operator, $C$ is lax monoidal with respect to $\meet$ (i.e.~$C(P) \meet C(Q) \sqleq C(P \meet Q)$),
and $C$ is lax strong, i.e.~$C(P) \meet Q \sqleq C(P \meet Q)$. $C$ being a fibred functor means it commutes
with any reindexing functor $\reindex{-}{f}$, i.e.~$C_X \comp \reindex{-}{f} \iso \reindex{-}{f} \comp C_Y$.
